---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

# Data exploration and cleaning

The first task in a data science project is data acquisition and cleaning. After a visual exploration of features we will be able to discard invalid data, fix errors and transform variables to make easier the modelization process.

### Loading required libraries
Some of the required data wrangling is easier to do using additional libraries beyond $R$ base like `data.table` or `tidyverse` for working with data frames, `lubridate` dor times and dates, or `forcats` for categorical data. Let's go to load into the environment.

```{r}
# Required libraries
listPackages <- c('data.table', 'tidyverse', 'lubridate', 'funModeling', 'forcats')
newPackages <- listPackages[!(listPackages %in% installed.packages()[,'Package'])]
if(length(newPackages)) install.packages(newPackages)

rm(list = c('listPackages', 'newPackages'))

library(data.table)
library(tidyverse)
library(lubridate)
library(funModeling)
library(forcats)
```

```{r}
# Download dataset from Dropbox
download.file(url = "https://www.dropbox.com/s/3802ph0qspdgtao/autos.csv?dl=1",
              destfile = '../data/autos.csv')
download.file(url = "https://www.dropbox.com/s/uzzhu05061xjm0z/zipcodes_de_completo.csv?dl=1",
              destfile = '../data/zipcodes_de_completo.csv')
```

